Temporal trends (NAMCS)

### 2017-07-24 ms1/namcs_trends.Rmd
validity checks

@@

@@

@@

x %>%
  select(abx, ci_low, pct_change, ci_high, p.value, adj.p.value) %>%
  mutate(sig=if_else(adj.p.value < 0.05, '*', '')) %>%
  kable
```

@@

```{r per_capita_models_display}
x = per_capita %>%
  filter(term=='year') %>%
  mutate(adj.p.value=p.adjust(p.value, method='BH')) %>%
  add_pct_change()

read_tsv('tables/model_abx.tsv') %>%
  filter(term=='year', model=='poisson') %>%
  left_join(top_abx, by=c('antibiotic'='medicare_abx')) %>%
  mutate(abx=if_else(is.na(abx), antibiotic, abx)) %>%
  mutate(data_source='medicare') %>%
  bind_rows(per_capita %>% filter(term=='year') %>% mutate(data_source='namcs')) %>%
  add_pct_change() %>%
  mutate(abx=forcats::fct_reorder(abx, pct_change)) %>%
  ggplot(aes(x=abx, y=pct_change, ymin=ci_low, ymax=ci_high, color=data_source)) +
  geom_linerange() +
  geom_point() +
  coord_flip() +
  xlab('') +
  ylab('pct change in consumption per capita') +
  ggtitle('Per capita') +
  theme_minimal()

x %>%
  select(abx, ci_low, pct_change, ci_high, p.value, adj.p.value) %>%
  arrange(desc(pct_change)) %>%
  kable
```

>>>>

## Data validity

The NAMCS methodology recommends that a value be considered sensible only if
(*a*) there are 30 records to support it and (*b*) and standard error is no
more than 30% of the estimate. There are at least 30 records per antibiotic per
year:

```{r data_validity}
visits %>%
  select(year, amox:tmpsmx) %>%
  group_by(year) %>%
  summarize_all(function(x) sum(x > 0)) %>%
  kable
```

@@

Levofloxacin has the largest apparent increase per visit (i.e., the number of
visits in which levofloxacin was prescribed increases the most).

@@

Levofloxacin and amox/clav have statistically significant results, as reported
by the Poisson regressions. Only the levofloxacin result meets the standard
error criterion for data validity.

@@

x %>%
  mutate(valid=abs(std.error/estimate)<=0.3, sig=if_else(adj.p.value < 0.05, '*', '')) %>%
  select(abx, ci_low, pct_change, ci_high, p.value, adj.p.value, valid, sig) %>%
  kable
```

@@

The trends in consumption per capita are all consistent with those observed in
Medicare, but none of them meet the standard error criterion for validity or
are statistically significant.

```{r per_capita_models_display}
x = per_capita %>%
  filter(term=='year') %>%
  mutate(valid=abs(std.error/estimate)<=0.3, adj.p.value=p.adjust(p.value, method='BH')) %>%
  add_pct_change()

read_tsv('tables/model_abx.tsv') %>%
  filter(term=='year', model=='poisson') %>%
  left_join(top_abx, by=c('antibiotic'='medicare_abx')) %>%
  mutate(abx=if_else(is.na(abx), antibiotic, abx)) %>%
  mutate(data_source='medicare') %>%
  bind_rows(per_capita %>% filter(term=='year') %>% mutate(data_source='namcs')) %>%
  add_pct_change() %>%
  mutate(abx=forcats::fct_reorder(abx, pct_change)) %>%
  ggplot(aes(x=abx, y=pct_change, ymin=ci_low, ymax=ci_high, color=data_source)) +
  #geom_linerange() +
  geom_errorbar() +
  geom_point() +
  coord_flip() +
  xlab('') +
  ylab('pct change in consumption per capita') +
  ggtitle('Per capita') +
  theme_minimal()

x %>%
  select(abx, ci_low, pct_change, ci_high, p.value, valid, adj.p.value) %>%
  arrange(desc(pct_change)) %>%
  kable
```
